Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-11-29 paper/main.tex
remove supplement part of imaging-based metric

%###################################################################################################
\subsection{Details for the Image-Space Metric}
\label{sec:supplement-comparison-algorithms}

In a different approach, one might be tempted to utilize the previously constructed direct
comparison algorithm for time intervals that do not contain any division events.
But this attempt would quickly lead to multiple problems.
It will not be able to deal with the uncertainties of the timing of the division event.
As the number of investigated cells grows, more division events will occurr even in a fixed
amount of time thus greatly decreasing or completely vanishing the effective interval at which no
division event is observed.
The latter situation is equivalent to two microscopic images as input data between which a division
event has occured.

%###################################################################################################
\subsection{Experimental Setup of Amir et. al}

>>>>

%###################################################################################################
\paragraph*{Experimental Setup of Amir et. al}
